Verifying Cache Coherence Protocols for an Infinite Family of Cache Hierarchies

### 2014-02-06 paper/Intuition.tex
fixed added one line in system

We first reduce the proof of store atomicity to 4 invariants, presented in
Section \ref{firstLevel}. These invariants in turn can be reduced to 4 more
invariants presented in Section \ref{secondLevel}. The reason for choosing the 8
 invariants is because they are not specific to the MSI protocol;
any other protocol that obeys these invariants obeys Theorem
\fullref{storeAtomicity}. We finally present the key insight that we
discovered for proving the second-level invariants in the form of 3 invariants.
We believe that other invalidation-based protocols with inclusive caches (\ie{}
those cache hierarchies where a parent cache contains all the locations that
any of its children contains) like MESI, MOSI and MOESI also
satisfy these 3 fundamental properties, making their verification easier by reusing
portions of our MSI proof.
We informally show why this is the case using the examples of MESI,
MOSI and MOESI in Section \ref{sec:Refinements}.
\adamc{...and maybe we don't, for space reasons. \texttt{:-)}}

@@

Proving the other 3 invariants in Section \ref{secondLevel} requires using
more properties of the MSI transistions of Figure~\ref{trans}, though the argument is
straightforward. Analyzing a parent-child pair will suffice in proving Invariants~
\fullref{localCompatibility1} and \fullref{localCompatibility2}. Proof of Invariant~
\fullref{noTransitWrite} is similar to the proof of Invariant~
\fullref{nonAncestorCompatible}.

@@

%initialization conditions described in Section \ref{System}. No response would

>>>>

We first reduce the proof of store atomicity to 4 invariants, presented in
Section~\ref{firstLevel}. These invariants in turn can be reduced to 4 more
invariants presented in Section~\ref{secondLevel}. The reason for choosing the 8
 invariants is because they are not specific to the MSI protocol;
any other protocol that obeys these invariants obeys Theorem
\fullref{storeAtomicity}. We finally present the key insight that we
discovered for proving the second-level invariants in the form of 3 invariants.
We believe that other invalidation-based protocols with inclusive caches (\ie{}
those cache hierarchies where a parent cache contains all the locations that
any of its children contains) like MESI, MOSI and MOESI also
satisfy these 3 fundamental properties, making their verification easier by reusing
portions of our MSI proof.
We informally show why this is the case using the examples of MESI,
MOSI and MOESI in Section~\ref{sec:Refinements}.
\adamc{...and maybe we don't, for space reasons. \texttt{:-)}}

@@

Proving the other 3 invariants in Section~\ref{secondLevel} requires using
more properties of the MSI transistions of Figure~\ref{trans}, though the argument is
straightforward. Analyzing a parent-child pair will suffice in proving Invariants~
\fullref{localCompatibility1} and \fullref{localCompatibility2}. Proof of Invariant~
\fullref{noTransitWrite} is similar to the proof of Invariant~
\fullref{nonAncestorCompatible}.

@@

%initialization conditions described in Section~\ref{System}. No response would
